---
title: "simpleRegress"
author: "Th3b0yn3xtd00r"
date: "Summer 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model LENGTH ~ NECK  this is an example  

We are going to compute regression models finding one regression model that does the best job in predicting the bear length and its correspondence to the bears neck size, age, head width, head length, chest, and WEIGHT

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

The adjusted r squared for the neck size is 0.7476.

## Compare all models that predict LENGTH other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 

```{r}
simp <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simp)
summary.lm(simp)
```

The adjusted r squared for HEADLEN is 0.8434.

```{r}
simp <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(simp)
summary.lm(simp)
```

The adjusted r squared for HEADWTH is 0.5321.

```{r}
simp <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(simp)
summary.lm(simp)
```

The adjusted r squared for AGE is 0.5073.

```{r}
simp <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simp)
summary.lm(simp)
```

The adjusted r squared for WEIGHT is 0.7423.

```{r}
simp <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simp)
summary.lm(simp)
```

The adjusted r squared for CHEST is 0.7869.

## Disscussion and Conclusion

In our report We are computing regression models and finding one regression model that does the best job in predicting the bear length and its correspondence to the bears neck size, age, head width, head length, chest, and WEIGHT while organizing which is smallest to largest? We are analyzing the adjusted r-squared for bear's characteristics for it's AGE, Neck size, Weight, Head Length, Head width, and Chest. I found that that overall best and largest is the Head length (0.8434). And in order from smallest to largest is Age (0.5073), then Head width (0.5321), then Weight (0.7423), then Neck size (0.7476), then Chest (0.7869), then finally the largest and best which is Head length (0.8434).
